FTLR proof cases

### 2018-03-12 fully-abstract-comp/ftlr-proof-cases.tex

@@

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
\[
  \npair{(\baddr,\eaddr)}\in \readCond{\lin,W}
  \npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}
\]
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lre(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{[(c,c)]} \in \lrp(W)$ \dominique{Weird that this is an assumption here.  Shouldn't this be a proof obligation? Or rather: I think this should not be here at all but in the value relation instead? Remove this from the definition of $\lre$?}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined\label{item:worlds-def}
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\updReg{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\updReg{\pcreg}{c})$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S,\Phi_T)} \in \lro
\]
Let $i \leq n'$ be given \footnote{ignoring the frame...} and show
\[
  \Phi_S \term[i] \Rightarrow \Phi_T \term
\]
and 
\[
  \Phi_T \term[i] \Rightarrow \Phi_S \term
\]

@@

We know that $\Phi_S(\pcreg) = \Phi_T(\pcreg) = c$, $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$, $\npair{(\baddr,\eaddr)}\in \readCond{\lin,W}$ and $\npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}$.
From Lemmas~\ref{lem:readcond-writecond-work}, using $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$ (from assumption~\ref{item:mem-ass}) and $W \oplus W_R \oplus W_M$ is well-defined (assumption~\ref{item:worlds-def}), we get (for any $a' \in [\baddr,\eaddr]$) that $\npair[n']{(\ms_S(a'),\ms_T(a'))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.

@@

\paragraph{Case: $\protect\tjmp{\trg{r_1}}$}

\paragraph{Case: $\protect\tjnz{\trg{r_1}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tisptr{\trg{r_1}}{\trg{r_2}}$}

\paragraph{Case: $\protect\tgeta{\trg{r_1}}{\trg{r_2}}$}
Similar to the case for $\tisptr{\trg{r_1}}{\trg{r_2}}$.

\paragraph{Case: $\protect\tgetb{\trg{r_1}}{\trg{r_2}}$}
Similar to the case for $\tisptr{\trg{r_1}}{\trg{r_2}}$.

\paragraph{Case: $\protect\tgete{\trg{r_1}}{\trg{r_2}}\mid$}
Similar to the case for $\tisptr{\trg{r_1}}{\trg{r_2}}$.

\paragraph{Case: $\protect\tgetlin{\trg{r_1}}{\trg{r_2}}$}
Similar to the case for $\tisptr{\trg{r_1}}{\trg{r_2}}$.

\paragraph{Case: $\protect\tmove{\trg{r_1}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tstore{\trg{r_1}}{\trg{r_2}}$}

\paragraph{Case: $\protect\tload{\trg{r_1}}{\trg{r_2}}$}

\paragraph{Case: $\protect\tcca{\trg{r_1}}{\trg{\rn}}$}

\paragraph{Case: $\protect\trestrict{\trg{r_1}}{\trg{r_2}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tlt{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tplus{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tminus{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tsetatob{\trg{r_1}}{\trg{r_2}}$}

@@

\paragraph{Case: $\protect\tcseal{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}$}

\paragraph{Case: $\protect\tsplit{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tsplice{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}$}

>>>>

\begin{lemma}
  \label{lem:stareg-ms-subeq-stdreg}
  If
  \begin{itemize}
  \item $R \nequal \stareg[(\ms,\ms)]{\pur}$
  \item $\npair{(\ms,\ms)} \in H^{\mathrm{std}}_{\dom(\ms)} \; * \; W$
  \item $\dom(\ms) \supseteq [\baddr,\eaddr]$
  \end{itemize}
  Then
  $R \nsubeq \stdreg{\dom(\ms)}{\pur}$
\end{lemma}
\begin{proof}
  \dominique{TODO: define nsubeq and friends first?}
\end{proof}

\begin{lemma}[readXCondition implies readCondition]
  \label{lem:readXCond-readCond}
  If $\npair{(\baddr,\eaddr)}\in\xReadCond{\lin,W}$, then $\npair{(\baddr,\eaddr)}\in\readCond{\lin,W}$.
\end{lemma}
\begin{proof}
  From $\npair{(\baddr,\eaddr)}\in\xReadCond{\lin,W}$, we get by definition an $r \in \addressable{\lin, \pwheap}$ and an $\ms$ with $\dom(\ms) \supseteq [\baddr,\eaddr]$,  $\npair{(\ms,\ms)} \in H^{\mathrm{std}}_{\dom(\ms)} \; * \; W$ and $\pwheap(r) \nequal \stareg[(\ms,\ms)]{\pur}$.

  The result then follows directly using Lemma~\ref{lem:stareg-ms-subeq-stdreg}.
\end{proof}

@@

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
\[
  \npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}
\]
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lre(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{[(c,c)]} \in \lrp(W)$ 
\dominique{Weird that this is an assumption here.  Shouldn't this be a proof obligation? Or rather: I think this should not be here at all but in the value relation instead? Remove this from the definition of $\lre$?}
\lau{$(c,c)$ is not shown or assumed to be in the value relation, so to make sure it respects lineraity, this condition is placed here. Further, this does become a proof obligation when you use the FTLR.}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined\label{item:worlds-def}
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\updReg{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\updReg{\pcreg}{c})$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S,\Phi_T)} \in \lro
\]
Let $i \leq n'$ be given \footnote{ignoring the frame...} and show
\[
  \Phi_S \term[i] \Rightarrow \Phi_T \term
\]
and 
\[
  \Phi_T \term[i] \Rightarrow \Phi_S \term
\]

@@

We know that $\Phi_S(\pcreg) = \Phi_T(\pcreg) = c$, $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$ and $\npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}$.
From Lemmas~\ref{lem:readcond-writecond-work} and~\ref{lem:readXCond-readCond}, using $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$ (from assumption~\ref{item:mem-ass}) and $W \oplus W_R \oplus W_M$ is well-defined (assumption~\ref{item:worlds-def}), we get (for any $a' \in [\baddr,\eaddr]$) that $\npair[n']{(\ms_S(a'),\ms_T(a'))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.

@@

\paragraph{Case: $\protect\tjmp{\trg{r}}$}

\paragraph{Case: $\protect\tjnz{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tisptr{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tgeta{\trg{r}}{\trg{r}}$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tgetb{\trg{r}}{\trg{r}}$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tgete{\trg{r}}{\trg{r}}\mid$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tgetlin{\trg{r}}{\trg{r}}$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tmove{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tstore{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tload{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tcca{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\trestrict{\trg{r}}{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tlt{\trg{r}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tsetatob{\trg{r}}{\trg{r}}$}

@@

\paragraph{Case: $\protect\tcseal{\trg{r}}{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tsplit{\trg{r}}{\trg{r}}{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tsplice{\trg{r}}{\trg{r}}{\trg{r}}$}
